---
title: "Amber & Brom MSc data combined"
author: "Will A. S. Hardy"
date: "08/11/2020"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
opts <- options(knitr.kable.NA = "")

##### Packages #####
library(brms) # for the analysis
library(haven) # to load the SPSS .sav file
library(tidyverse) # needed for data manipulation.
library(RColorBrewer) # needed for some extra colours in one of the graphs
library(ggmcmc)
library(ggthemes)
library(ggridges)
library(RcppEigen)
library(knitr)

options(mc.cores = parallel::detectCores() - 1)

##### Data #####
amber_brom1 <- read_rds("../data/amber_brom_msc_merged.rds")

small_team <- 
  amber_brom1 %>% 
  group_by(team) %>% 
  count() %>% 
  arrange(n) %>% 
  filter(n < 5) %>% 
  .$team

amber_brom <- 
  amber_brom1 %>% 
  filter(!team %in% small_team)

amber_brom_centered <-
  amber_brom %>%
  left_join(amber_brom %>% group_by(team) %>%
              summarise(team_npi = mean(npi_mean, na.rm = TRUE), # create team means
                        team_cni = mean(cni_mean, na.rm = TRUE),
                        sd_npi = sd(npi_mean, na.rm = TRUE),
                        sd_cni = sd(cni_mean, na.rm = TRUE)),
            by = "team") %>% 
  mutate(npi_mean = npi_mean - team_npi, # centre individual IV scores on team mean
         cni_mean = cni_mean  - team_cni,
         team_npi = team_npi - mean(team_npi, na.rm = TRUE),
         team_cni = team_cni - mean(team_cni, na.rm = TRUE))


#### Functions ####
# To colour code the extremes, we need to write a small function that calculates the regression lines and adds a column indicating which clusters have the most extreme.
f1 <- function(data, x, y, grouping, n.highest = 3, n.lowest = 3){
  groupinglevel <- data[,grouping]
  res           <- data.frame(coef = rep(NA, length(unique(groupinglevel))), group = unique(groupinglevel))
  names(res)    <- c("coef", grouping)
  for(i in 1:length(unique(groupinglevel))){
    data2    <- as.data.frame(data[data[,grouping] == i,])
    res[i,1] <- as.numeric(lm(data2[, y] ~ data2[, x])$coefficients[2])
  }
  top    <- res %>% top_n(n.highest, coef)
  bottom <- res %>% top_n(-n.lowest, coef)
  res    <- res %>% mutate(high_and_low = ifelse(coef %in% top$coef, "top",  ifelse(coef %in% bottom$coef, "bottom", "none")))
  data3  <- left_join(data, res)
  return(data3)
}

modelParams <- function(model){
  posterior_summary(model) %>% 
  as_tibble(rownames = NA) %>% 
  rownames_to_column(var = "Parameter") %>% 
  filter(!str_detect(Parameter, "r_team"),
         !str_detect(Parameter, "L_"),
         !str_detect(Parameter, "z_"))
}

bayesEstimate <- function(.){
  require(papaja)
  paste0(printnum(.$Estimate), "[", printnum(.$Q2.5), ",", printnum(.$Q97.5), "]")
}
```


## Team level summary

```{r}
amber_brom_centered %>% 
  group_by(team) %>% 
  summarise(across(.cols = where(is.numeric), .fns = ~mean(.x, na.rm = TRUE))) %>% 
  kable(digits = 2)
```


## Group goal commitment {.tabset}
### Plotting the data {.tabset}
#### Scatter

```{r}
## scatter
ggplot(data  = amber_brom,
       aes(x = npi_mean,
           y = ggc_mean))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  theme_minimal()+
  labs(title = "NPI narcissism vs. Group conflict")
```


#### Scatter with regression line

```{r}
ggplot(data  = amber_brom,
       aes(x = npi_mean,
           y = ggc_mean))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  geom_smooth(method = lm,
              se     = FALSE,
              col    = "black",
              size   = .5,
              alpha  = .8)+ # to add regression line
  theme_minimal()+
  labs(title = "NPI narcissism vs. Group conflict",
       subtitle = "add regression line")
```


#### Scatter with regression line by sex

```{r}
ggplot(data  = amber_brom,
       aes(x = npi_mean,
           y = ggc_mean,
           col = sex,
           group = sex))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  geom_smooth(method = lm,
              # se     = FALSE,
              # col    = "black",
              size   = .5,
              alpha  = .8)+ # to add regression line
  theme_minimal()+
  labs(title = "NPI narcissism vs. Group conflict",
       subtitle = "add regression line")
```


#### Scatter with regression lines coloured by team

##### NPI

```{r}
ggplot(data  = amber_brom,
       aes(x = npi_mean,
           y = ggc_mean,
           col = as.numeric(team),
           group = team)) +
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter") +# to add some random noise for plotting purposes
  theme_minimal() +
  theme(legend.position = "none") +
  scale_color_gradientn(colours = rainbow(59)) +
  geom_smooth(method = lm,
              se     = FALSE,
              size   = .5,
              alpha  = .8) + # to add regression line
  labs(title = "NPI narcissism vs. Group goal commitment",
       subtitle = "add colours and regression lines for different teams")
```


##### CNI

```{r}
ggplot(data  = amber_brom,
       aes(x = cni_mean,
           y = ggc_mean,
           col = as.numeric(team),
           group = team)) +
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter") +# to add some random noise for plotting purposes
  theme_minimal() +
  theme(legend.position = "none") +
  scale_color_gradientn(colours = rainbow(59)) +
  geom_smooth(method = lm,
              se     = FALSE,
              size   = .5,
              alpha  = .8) + # to add regression line
  labs(title = "CNI narcissism vs. Group goal commitment",
       subtitle = "add colours and regression lines for different teams")
```


### Analysis 1 {.tabset}
#### Intercept only model

```{r, include=FALSE}
ggc_interceptonlymodel <- 
  brm(ggc_mean ~ 1 + (1|team),  
      data = na.omit(select(amber_brom_centered, ggc_mean,
                            team_npi, team_cni, team, npi_mean, cni_mean,)), 
      warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

ggc_interceptonlyparams <- modelParams(ggc_interceptonlymodel)

# Calculating ICC
hyp <- "sd_team__Intercept^2 / (sd_team__Intercept^2 + sigma^2) = 0"
icc_test <- print(hypothesis(ggc_interceptonlymodel, hyp, class = NULL))
icc_est <- paste0(icc_test$hypothesis$Estimate, " [", icc_test$hypothesis$CI.Lower, ",",
       icc_test$hypothesis$CI.Upper, "]")
```


```{r}
ggc_interceptonlyparams %>% 
  kable(digits = 2)
```

* Posterior mean of residual variance at team level = `r ggc_interceptonlyparams[2,2]^2`
* Posterior mean of residual variance at individual level = `r ggc_interceptonlyparams[3,2]^2`
* ICC: $\rho$ = `r icc_est`


#### First level predictors no interaction

```{r, m0-est, interval=FALSE}
ggc_model0 <- brm(ggc_mean ~ 1 + sex + npi_mean + cni_mean + (1|team),  
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

ggc_model0params <- modelParams(ggc_model0)
```

```{r, m0-print}
ggc_model0params %>% 
  kable(digits = 2)
```

* Fixed regression slopes are not different to 0
* Residual variance on the team level is small: $\sigma_{u0}$ = `r ggc_model0params[6,2]^2`)



#### First level predictors

```{r, interval=FALSE}
ggc_model1 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + (1|team),  
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

ggc_model1params <- modelParams(ggc_model1)
```

```{r}
ggc_model1params %>% 
  kable(digits = 2)
```

* Fixed regression slopes are not different to 0
* Residual variance on the team level is small: $\sigma_{u0}$ = `r ggc_model1params[6,2]^2`)


#### First and second level predictors

```{r, include=FALSE}
ggc_model2 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni + (1|team),
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE)

ggc_model2params <- modelParams(ggc_model2)

ggc_L1R2 <- 
  # Because the variables have been centred on the group means, the sigma^2 is
    # a biased estimator. Snijders & Bosker (2012) suggest incorporating the 
    # variance of the intercept to use the within-group variance in a consistent
    # way
  ((ggc_interceptonlyparams[3,2]^2 + ggc_interceptonlyparams[2,2]^2) - 
  (ggc_model2params[9,2]^2 + ggc_model2params[8,2]^2)) / 
  (ggc_interceptonlyparams[3,2]^2 + ggc_interceptonlyparams[2,2]^2)

# Muthen (1994) ad hoc estimator to replace n in Snijders & Boskers's (1994)
  # fix for L2 R2 estimate
grp_sizes <- 
  amber_brom_centered %>% 
  group_by(team) %>% 
  summarise(n = n(),
            nsq = n()^2)

c <- (nrow(amber_brom_centered)^2 - sum(grp_sizes$nsq)) / 
  (nrow(amber_brom_centered) * length(unique(amber_brom_centered$team)) - 1)

ggc_L2R2 <- ((ggc_interceptonlyparams[2,2]^2 + ggc_interceptonlyparams[3,2]^2/c) - 
           (ggc_model2params[8,2]^2 + ggc_model2params[9,2]^2/c)) / 
  (ggc_interceptonlyparams[2,2]^2 + ggc_interceptonlyparams[3,2]^2/c)
  
```

```{r}
ggc_model2params %>% 
  kable(digits = 2)
```

* sexMale is greater than 0 
* team_npi is less than 0
* Residual variance on the team level is small: $\sigma_{u0}$ = `r ggc_model2params[8,2]^2`)
* L1 $R^2$ = `r ggc_L1R2`
* L2 $R^2$ = `r ggc_L2R2`

#### First and second level predictors with random slopes

```{r, include=FALSE}
ggc_model3 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi + team_cni|team),
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE)

ggc_model3params <- modelParams(ggc_model3)
```


```{r}
ggc_model3params %>% 
  kable(digits = 2)

broom.mixed::tidy(ggc_model3)
```

* sexMale is greater than zero
* team_npi is less than 0
* all random slopes variances, except `team_cni`, are greater than zero
  * remove random slope for `team_cni`
  
```{r, include=FALSE}
ggc_model4 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi |team),
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE)

ggc_model4params <- modelParams(ggc_model4)
```


```{r}
ggc_model4params %>% 
  kable(digits = 2)
```

* random slope for `cni_mean` not different to zero but random slope for npi_mean:cni_mean is, therefore retain

#### First and second level predictors without interaction and with random slopes

```{r, include=FALSE}
ggc_model3.1 <- brm(ggc_mean ~ 1 + sex + npi_mean + cni_mean + 
                team_npi + team_cni + 
                (1 + sex + npi_mean + cni_mean + team_npi + team_cni|team),
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE)

ggc_model3.1params <- modelParams(ggc_model3.1)
```


```{r}
ggc_model3.1params %>% 
  kable(digits = 2)

broom.mixed::tidy(ggc_model3.1)
```


#### First and second level predictors with random slopes and cross-level interaction

```{r, include=FALSE}
ggc_model5 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni +
                team_npi*team_cni:npi_mean*cni_mean +
                (1 + sex + npi_mean*cni_mean + team_npi|team),
              data = amber_brom_centered, 
              warmup = 3000, iter = 8000, save_all_pars = TRUE,
              seed = 123, control = list(adapt_delta = 0.99))

ggc_model5params <- modelParams(ggc_model5)
```


```{r}
ggc_model5params %>% 
  kable(digits = 2)

conditional_effects(ggc_model5)

```

* The estimate for the intercept is 0.65[-0.68;2.00] NS
* The estimate for the fixed effect of sex (Male) is 0.31[0.05;0.57]


#### First and second level predictors with random slopes and full cross-level interaction

```{r, include=FALSE}
ggc_model6 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni +
                team_npi*team_cni*npi_mean*cni_mean +
                (1 + sex + npi_mean*cni_mean + team_cni*team_npi|team),
              data = amber_brom_centered, 
              warmup = 3000, iter = 8000, save_all_pars = TRUE,
              seed = 123, control = list(adapt_delta = 0.99))

ggc_model6params <- modelParams(ggc_model6)
```


```{r}
ggc_model6params %>% 
  kable(digits = 2)

conditional_effects(ggc_model6)
```

### Model comparison 1

```{r}
ggc_interceptestimates <- 
  ggc_interceptonlyparams %>% 
  transmute(Parameter = Parameter,
            `Intercept only` = bayesEstimate(.))
ggc_model1estimates <- 
  ggc_model1params %>% 
  transmute(Parameter = Parameter,
            `L1 predictors` = bayesEstimate(.))
ggc_model2estimates <- 
  ggc_model2params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors` = bayesEstimate(.))
ggc_model3estimates <- 
  ggc_model3params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors and random slopes 1` = bayesEstimate(.))
ggc_model3.1estimates <- 
  ggc_model3.1params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors and random slopes 1 no interaction` = bayesEstimate(.))
ggc_model4estimates <- 
  ggc_model4params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors and random slopes 2` = bayesEstimate(.))
ggc_model5estimates <- 
  ggc_model5params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors and random slopes 2 with cross level interaction` = bayesEstimate(.))

full_join(x = tibble(Parameter = ggc_model5estimates$Parameter), 
          y = ggc_interceptestimates, by = "Parameter") %>% 
  full_join(ggc_model1estimates, 
            by = "Parameter", suffix = c(".I", ".1")) %>% 
  full_join(ggc_model2estimates, 
            by = "Parameter", suffix = c("", ".2")) %>% 
  full_join(ggc_model3estimates, 
            by = "Parameter", suffix = c("", ".3")) %>% 
  full_join(ggc_model3.1estimates, 
            by = "Parameter", suffix = c("", ".3.1")) %>% 
  full_join(ggc_model4estimates, 
            by = "Parameter", suffix = c("", ".4")) %>% 
  # full_join(ggc_model4.1estimates, 
  #           by = "Parameter", suffix = c("", ".4.1")) %>% 
  full_join(ggc_model5estimates, 
            by = "Parameter", suffix = c("", ".5")) %>% 
  select(-c(starts_with("Est.Error"))) %>%
  filter(!Parameter == "lp__" &
           str_detect(Parameter, "z_") == FALSE &
           str_detect(Parameter, "r_") == FALSE &
           str_detect(Parameter, "L_") == FALSE) %>% 
  kable(align = "r")

# full_join(
#   x = full_join(
#     x = full_join(x = tibble(Parameter = ggc_model5estimates$Parameter), 
#                   y = ggc_interceptestimates, by = "Parameter"), 
#     y = ggc_model1estimates, 
#     by = "Parameter", suffix = c(".I", ".1")),
#   y = full_join(ggc_model2estimates, ggc_model3estimates, by = "Parameter", suffix = c(".2", ".3"))) %>%  
#   full_join(full_join(ggc_model4estimates, ggc_model5estimates, by = "Parameter", suffix = c(".4", ".5")),
#             by = "Parameter") 
```


```{r, message = FALSE}
crit <- c('loo', 'waic', 'kfold', 'loo_subsample', 'bayes_R2', 'loo_R2', 'marglik')
ggc_interceptonlymodel <- add_criterion(ggc_interceptonlymodel, crit)
ggc_model1 <- add_criterion(ggc_model1, crit)
ggc_model2 <- add_criterion(ggc_model2, crit)
ggc_model3 <- add_criterion(ggc_model3, crit)
ggc_model4 <- add_criterion(ggc_model4, crit)
ggc_model5 <- add_criterion(ggc_model5, crit)

ggc_loo1 <- loo(ggc_interceptonlymodel)
ggc_loo2 <- loo(ggc_model1)
ggc_loo3 <- loo(ggc_model2)
ggc_loo4 <- loo(ggc_model3)
ggc_loo5 <- loo(ggc_model4)
ggc_loo6 <- loo(ggc_model5)
ggc_loo7 <- loo_compare(ggc_interceptonlymodel, ggc_model1, ggc_model2, ggc_model3, 
                ggc_model4, ggc_model5, criterion = "loo")

ggc_loo7

print(mean(ggc_model3$criteria$bayes_R2))
print(mean(ggc_model5$criteria$bayes_R2))
```



### Analysis 2 {.tabset}
#### Intercept only model

```{r, include=FALSE}
ggc2_interceptonlymodel <- 
  brm(ggc_mean ~ 1 + (1|team),  
      data = na.omit(select(amber_brom_centered, ggc_mean,
                            team_npi, team_cni, team, npi_mean, cni_mean,)), 
      warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

ggc2_interceptonlyparams <- modelParams(ggc2_interceptonlymodel)

# Calculating ICC
hyp <- "sd_team__Intercept^2 / (sd_team__Intercept^2 + sigma^2) = 0"
icc_test <- print(hypothesis(ggc2_interceptonlymodel, hyp, class = NULL))
icc_est <- paste0(icc_test$hypothesis$Estimate, " [", icc_test$hypothesis$CI.Lower, ",",
       icc_test$hypothesis$CI.Upper, "]")
```


```{r}
ggc2_interceptonlyparams %>% 
  kable(digits = 2)
```

* Posterior mean of residual variance at team level = `r ggc2_interceptonlyparams[2,2]^2`
* Posterior mean of residual variance at individual level = `r ggc2_interceptonlyparams[3,2]^2`
* ICC: $\rho$ = `r icc_est`


#### First level predictors

```{r, interval=FALSE}
ggc2_model1 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + (1|team),  
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

ggc2_model1params <- modelParams(ggc2_model1)
```

```{r}
ggc2_model1params %>% 
  kable(digits = 2)
```

* Fixed regression slopes are not different to 0
* Residual variance on the team level is small: $\sigma_{u0}$ = `r ggc2_model1params[6,2]^2`)


#### First and second level predictors

```{r, include=FALSE}
ggc2_model2 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                     team_npi + team_cni + sd_npi + sd_cni + (1|team),
                   data = amber_brom_centered, 
                   warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE)

ggc2_model2params <- modelParams(ggc2_model2)

ggc2_L1R2 <- 
  # Because the variables have been centred on the group means, the sigma^2 is
    # a biased estimator. Snijders & Bosker (2012) suggest incorporating the 
    # variance of the intercept to use the within-group variance in a consistent
    # way
  ((ggc2_interceptonlyparams[3,2]^2 + ggc2_interceptonlyparams[2,2]^2) - 
  (ggc2_model2params[9,2]^2 + ggc2_model2params[8,2]^2)) / 
  (ggc2_interceptonlyparams[3,2]^2 + ggc2_interceptonlyparams[2,2]^2)

# Muthen (1994) ad hoc estimator to replace n in Snijders & Boskers's (1994)
  # fix for L2 R2 estimate
grp_sizes <- 
  amber_brom_centered %>% 
  group_by(team) %>% 
  summarise(n = n(),
            nsq = n()^2)

c <- (nrow(amber_brom_centered)^2 - sum(grp_sizes$nsq)) / 
  (nrow(amber_brom_centered) * length(unique(amber_brom_centered$team)) - 1)

ggc2_L2R2 <- ((ggc2_interceptonlyparams[2,2]^2 + ggc2_interceptonlyparams[3,2]^2/c) - 
           (ggc2_model2params[8,2]^2 + ggc2_model2params[9,2]^2/c)) / 
  (ggc2_interceptonlyparams[2,2]^2 + ggc2_interceptonlyparams[3,2]^2/c)
  
```

```{r}
ggc2_model2params %>% 
  kable(digits = 2)
```

* sexMale is greater than 0 
* team_npi is less than 0
* Residual variance on the team level is small: $\sigma_{u0}$ = `r ggc2_model2params[8,2]^2`)
* L1 $R^2$ = `r ggc2_L1R2`
* L2 $R^2$ = `r ggc2_L2R2`

#### First and second level predictors with random slopes

```{r, include=FALSE}
ggc2_model3 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                     team_npi + team_cni + sd_npi + sd_cni +
                     (1 + sex + npi_mean*cni_mean + 
                        team_npi + team_cni + sd_npi + sd_cni|team),
                   data = amber_brom_centered, 
                   control = list(adapt_delta = 0.99),
                   warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE)

ggc2_model3params <- modelParams(ggc2_model3)
```


```{r}
ggc2_model3params %>% 
  kable(digits = 2)

broom.mixed::tidy(ggc2_model3)
```

* sexMale is greater than zero
* team_npi is less than 0
* all random slopes variances, except `team_cni`, are greater than zero
  * remove random slope for `team_cni`
  
```{r, include=FALSE}
ggc2_model4 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi |team),
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE)

ggc2_model4params <- modelParams(ggc2_model4)
```


```{r}
ggc2_model4params %>% 
  kable(digits = 2)
```

* random slope for `cni_mean` not different to zero but random slope for npi_mean:cni_mean is, therefore retain


#### First and second level predictors with random slopes and cross-level interaction

```{r, include=FALSE}
ggc2_model5 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni +
                team_npi*team_cni:npi_mean*cni_mean +
                  sd_npi*(npi_mean*cni_mean) + sd_cni*(npi_mean*cni_mean)
                (1 + sex + npi_mean*cni_mean + team_cni + team_npi|team),
              data = amber_brom_centered, 
              warmup = 3000, iter = 8000, save_all_pars = TRUE,
              seed = 123, control = list(adapt_delta = 0.99))

ggc2_model5params <- modelParams(ggc2_model5)
```


```{r}
ggc2_model5params %>% 
  kable(digits = 2)

conditional_effects(ggc2_model5)

```

* The estimate for the intercept is 0.65[-0.68;2.00] NS
* The estimate for the fixed effect of sex (Male) is 0.31[0.05;0.57]


#### First and second level predictors with random slopes and full cross-level interaction

```{r, include=FALSE}
ggc2_model6 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni +
                team_npi*team_cni*npi_mean*cni_mean*sd_npi*sd_cni +
                (1 + sex + npi_mean*cni_mean + team_cni*team_npi + 
                   sd_npi + sd_cni|team),
              data = amber_brom_centered, 
              warmup = 3000, iter = 8000, save_pars = save_pars(all = TRUE),
              seed = 123, control = list(adapt_delta = 0.99))

ggc2_model6params <- modelParams(ggc2_model6)
```


```{r}
ggc2_model6params %>% 
  kable(digits = 2)

conditional_effects(ggc2_model6)
```

### Model comparison 2

```{r}
ggc2_interceptestimates <- 
  ggc2_interceptonlyparams %>% 
  transmute(Parameter = Parameter,
            `Intercept only` = bayesEstimate(.))
ggc2_model1estimates <- 
  ggc2_model1params %>% 
  transmute(Parameter = Parameter,
            `L1 predictors` = bayesEstimate(.))
ggc2_model2estimates <- 
  ggc2_model2params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors` = bayesEstimate(.))
ggc2_model3estimates <- 
  ggc2_model3params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors and random slopes 1` = bayesEstimate(.))
ggc2_model4estimates <- 
  ggc2_model4params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors and random slopes 2` = bayesEstimate(.))
ggc2_model5estimates <- 
  ggc2_model5params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors and random slopes 2 with cross level interaction` = bayesEstimate(.))

full_join(full_join(full_join(x = tibble(Parameter = ggc2_model5estimates$Parameter), 
                      y = ggc2_interceptestimates, by = "Parameter"), ggc2_model1estimates, 
                    by = "Parameter", suffix = c(".I", ".1")),
  full_join(ggc2_model2estimates, ggc2_model3estimates, by = "Parameter", suffix = c(".2", ".3"))) %>%  
  full_join(full_join(ggc2_model4estimates, ggc2_model5estimates, by = "Parameter", suffix = c(".4", ".5")),
    by = "Parameter") %>% 
  select(-c(starts_with("Est.Error"))) %>%
  filter(!Parameter == "lp__" &
           str_detect(Parameter, "z_") == FALSE &
           str_detect(Parameter, "r_") == FALSE &
           str_detect(Parameter, "L_") == FALSE) %>% 
  kable(align = "r")
```


```{r, message = FALSE}
crit <- c('loo', 'waic', 'kfold', 'loo_subsample', 'bayes_R2', 'loo_R2', 'marglik')
ggc2_interceptonlymodel <- add_criterion(ggc2_interceptonlymodel, crit)
ggc2_model1 <- add_criterion(ggc2_model1, crit)
ggc2_model2 <- add_criterion(ggc2_model2, crit)
ggc2_model3 <- add_criterion(ggc2_model3, crit)
ggc2_model4 <- add_criterion(ggc2_model4, crit)
ggc2_model5 <- add_criterion(ggc2_model5, crit)

ggc2_loo1 <- loo(ggc2_interceptonlymodel)
ggc2_loo2 <- loo(ggc2_model1)
ggc2_loo3 <- loo(ggc2_model2)
ggc2_loo4 <- loo(ggc2_model3)
ggc2_loo5 <- loo(ggc2_model4)
ggc2_loo6 <- loo(ggc2_model5)
ggc2_loo7 <- loo_compare(ggc2_interceptonlymodel, ggc2_model1, ggc2_model2, ggc2_model3, 
                ggc2_model4, ggc2_model5, criterion = "loo")

ggc2_loo7

print(mean(ggc2_model3$criteria$bayes_R2))
print(mean(ggc2_model5$criteria$bayes_R2))
```



## IGC multivariate {.tabset}

### Plotting

```{r, eval=TRUE}
plotSlopes <- function(data, resp, efflist, group) {
  require(ggplot2)
  require(purrr)
  y <- enquo(resp)
  group <- enquo(group)
  ngroups <- data %>% 
    select(!!group) %>% 
    unique() %>% 
    nrow()

  map(efflist, function(x)
    ggplot(data, aes(!!sym(x), !!y, col = as.numeric(!!group), 
                     group = !!group)) +
    geom_point(size = 1.2,
               alpha = .8,
               position = "jitter") + # to add some random noise for plotting purposes
    theme_minimal() +
    theme(legend.position = "none") +
    scale_color_gradientn(colours = rainbow(n = ngroups)) +
    geom_smooth(method = lm,
                se     = FALSE,
                size   = .5,
                alpha  = .8) + # to add regression line
    ylab(NULL)
  )
}
```


#### NPI

```{r}
plotSlopes(amber_brom, resp = npi_mean, 
           efflist = c("igc_task", "igc_rel", "igc_proc"),
           group = team) %>% 
  gridExtra::grid.arrange(grobs = ., left = "npi_mean")
```


#### CNI

```{r}
plotSlopes(amber_brom, resp = cni_mean, 
           efflist = c("igc_task", "igc_rel", "igc_proc"),
           group = team) %>% 
  gridExtra::grid.arrange(grobs = ., left = "cni_mean")
```



### Analysis {.tabset}
#### Intercept only model

try `capture.output()`

```{r, include=FALSE}
igc_interceptonlymodel <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + (1|p|team),  
                          data = amber_brom_centered, 
                          warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

# x <- sjstats::tidy_stan(interceptonlymodel, prob = .95)
# 
# bind_rows(x$fixed.conditional..igcproc,
# x$fixed.conditional..igcrel,
# x$fixed.sigma..igcrel,
# x$fixed.conditional..igctask,
# x$fixed.sigma..igctask
# ) %>% 
#   pivot_wider(id_cols = Cleaned_Parameter, names_from = Response, values_from = c(Estimate, Std.Error, `HDI(95%)`))
```


```{r}
igc_interceptonlyparams <- modelParams(igc_interceptonlymodel)

igc_interceptonlyparams %>% 
  kable(digits = 2)
```



#### First level predictors

```{r, include = FALSE}
igc_model1 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + (1|p|team), 
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

igc_model1params <- modelParams(igc_model1)
```


```{r}
igc_model1params %>% 
  kable(digits = 2)
```


#### First and second level predictors

```{r, include = FALSE}
igc_model2 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + team_npi + team_cni + (1|p|team), 
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

igc_model2params <- modelParams(igc_model2)
```


```{r}
igc_model2params %>% 
  kable(digits = 2)
```



#### First and second level predictors with L1 random slopes

```{r}
igc_model3 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + team_npi + team_cni + (1 + 
                sex + npi_mean * cni_mean|p|team), 
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

igc_model3params <- modelParams(igc_model3)
```


```{r}
igc_model3params %>% 
  kable(digits = 2)

conditional_effects(igc_model3)
```




#### First and level predictors with L1 interaction and L2 random slopes

```{r}
igc_model4 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + team_npi + team_cni + (1 + 
                sex + npi_mean * cni_mean + team_npi + team_cni|p|team), 
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123,
              control = list(adapt_delta = 0.99), save_all_pars = TRUE) 

igc_model4params <- modelParams(igc_model4)
```


```{r}
igc_model4params %>% 
  kable(digits = 2)

conditional_effects(igc_model4)
```


#### First and level predictors with L2 interaction and L2 random slopes

```{r}
igc_model5 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean*cni_mean + team_npi*team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi*team_cni|p|team), 
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123,
              control = list(adapt_delta = 0.99), save_all_pars = TRUE) 

igc_model5params <- modelParams(igc_model5)
```


```{r}
igc_model5params %>% 
  kable(digits = 2)

conditional_effects(igc_model5)
```
#### First and level predictors with L2 interaction and L2 random slopes and partial cross level interaction

```{r}
igc_model6 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean*cni_mean:team_npi*team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi*team_cni|p|team), 
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123,
              control = list(adapt_delta = 0.99), save_all_pars = TRUE) 

igc_model6params <- modelParams(igc_model6)
```


```{r}
igc_model6params %>% 
  kable(digits = 2)

conditional_effects(igc_model6)
```


#### First and level predictors with L2 interaction and L2 random slopes and full cross level interaction

```{r}
igc_model7 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean*cni_mean*team_npi*team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi*team_cni|p|team), 
              data = amber_brom_centered, 
              warmup = 1000, iter = 3000, seed = 123,
              control = list(adapt_delta = 0.99), save_all_pars = TRUE) 

igc_model7params <- modelParams(igc_model7)
```


```{r}
igc_model7params %>% 
  kable(digits = 2)

conditional_effects(igc_model7)
```



### Model comparison

```{r}
igc_interceptestimates <- 
  igc_interceptonlyparams %>% 
  transmute(Parameter = Parameter,
            `Intercept only` = bayesEstimate(.))
igc_model1estimates <- 
  igc_model1params %>% 
  transmute(Parameter = Parameter,
            `L1 predictors` = bayesEstimate(.))
igc_model2estimates <-
  igc_model2params %>% 
  transmute(Parameter = Parameter,
            `L2 predictors` = bayesEstimate(.))
igc_model3estimates <- 
  igc_model3params %>% 
  transmute(Parameter = Parameter,
            `L1 interaction` = bayesEstimate(.))
igc_model4estimates <- 
  igc_model4params %>% 
  transmute(Parameter = Parameter,
            `L1 interaction L1 random slopes` = bayesEstimate(.))
igc_model5estimates <- 
  igc_model5params %>% 
  transmute(Parameter = Parameter,
            `L1 interaction L2 random slopes` = bayesEstimate(.))


full_join(
  full_join(
    full_join(
      full_join(x = tibble(Parameter = igc_model5estimates$Parameter), 
                y = igc_interceptestimates, by = "Parameter"), igc_model1estimates, 
      by = "Parameter", suffix = c(".I", ".1")),
    full_join(igc_model2estimates, igc_model3estimates, by = "Parameter", 
              suffix = c(".2", ".3"))),
  full_join(igc_model4estimates, igc_model5estimates, by = "Parameter", 
            suffix = c(".4", ".5"))) %>%  
  select(-c(starts_with("Est.Error"))) %>%
  filter(!Parameter == "lp__" &
           str_detect(Parameter, "z_") == FALSE &
           str_detect(Parameter, "r_") == FALSE &
           str_detect(Parameter, "L") == FALSE) %>% 
  kable()
```
