---
title: "Amber data"
author: "Will A. S. Hardy"
date: "08/11/2020"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)

##### Packages #####
library(brms) # for the analysis
library(haven) # to load the SPSS .sav file
library(tidyverse) # needed for data manipulation.
library(RColorBrewer) # needed for some extra colours in one of the graphs
library(ggmcmc)
library(ggthemes)
library(ggridges)
library(RcppEigen)

##### Data #####
amber <- read_rds("../data/amber.rds")
amber_centered <-
  amber %>%
  mutate(npi_mean = npi_mean - mean(amber$npi_mean, na.rm = T),
         cni_mean = cni_mean - mean(amber$cni_mean, na.rm = T)) %>%
  left_join(amber %>% group_by(team) %>%
              summarise(team_npi = mean(npi_mean, na.rm = T),
                        team_cni = mean(cni_mean, na.rm = T)))
#group centred
    # left_join(amber %>% group_by(team) %>%
  #             summarise(team_npi = mean(npi_mean, na.rm = T),
  #                       team_cni = mean(cni_mean, na.rm = T))) %>% 
  # mutate(npi_mean = npi_mean - mean(amber$npi_mean, na.rm = T),
  #        cni_mean = cni_mean - mean(amber$cni_mean, na.rm = T),
  #        ggc_mean = ggc_mean - mean(amber$ggc_mean, na.rm = T),
  #        igc_rel = igc_rel - mean(amber$igc_rel, na.rm = T),
  #        igc_proc = igc_proc - mean(amber$igc_proc, na.rm = T),
  #        igc_task = igc_task - mean(amber$igc_task, na.rm = T))

#### Functions ####
# To colour code the extremes, we need to write a small function that calculates the regression lines and adds a column indicating which clusters have the most extreme.
f1 <- function(data, x, y, grouping, n.highest = 3, n.lowest = 3){
  groupinglevel <- data[,grouping]
  res           <- data.frame(coef = rep(NA, length(unique(groupinglevel))), group = unique(groupinglevel))
  names(res)    <- c("coef", grouping)
  for(i in 1:length(unique(groupinglevel))){
    data2    <- as.data.frame(data[data[,grouping] == i,])
    res[i,1] <- as.numeric(lm(data2[, y] ~ data2[, x])$coefficients[2])
  }
  top    <- res %>% top_n(n.highest, coef)
  bottom <- res %>% top_n(-n.lowest, coef)
  res    <- res %>% mutate(high_and_low = ifelse(coef %in% top$coef, "top",  ifelse(coef %in% bottom$coef, "bottom", "none")))
  data3  <- left_join(data, res)
  return(data3)
}
```

## Group goal commitment {.tabset}
### Plotting the data {.tabset}
#### Scatter

```{r}
## scatter
ggplot(data  = amber,
       aes(x = npi_mean,
           y = ggc_mean))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  theme_minimal()+
  labs(title = "NPI narcissism vs. Group conflict")
```


#### Scatter with regression line

```{r}
ggplot(data  = amber,
       aes(x = npi_mean,
           y = ggc_mean))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  geom_smooth(method = lm,
              se     = FALSE,
              col    = "black",
              size   = .5,
              alpha  = .8)+ # to add regression line
  theme_minimal()+
  labs(title = "NPI narcissism vs. Group conflict",
       subtitle = "add regression line")
```


#### Scatter with regression line by sex

```{r}
ggplot(data  = amber,
       aes(x = npi_mean,
           y = ggc_mean,
           col = sex,
           group = sex))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  geom_smooth(method = lm,
              # se     = FALSE,
              # col    = "black",
              size   = .5,
              alpha  = .8)+ # to add regression line
  theme_minimal()+
  labs(title = "NPI narcissism vs. Group conflict",
       subtitle = "add regression line")
```


#### Scatter with regression lines coloured by team

```{r}
ggplot(data  = amber,
       aes(x = npi_mean,
           y = ggc_mean,
           col = as.numeric(team),
           group = team)) +
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter") +# to add some random noise for plotting purposes
  theme_minimal() +
  theme(legend.position = "none") +
  scale_color_gradientn(colours = rainbow(59)) +
  geom_smooth(method = lm,
              se     = FALSE,
              size   = .5,
              alpha  = .8) + # to add regression line
  labs(title = "NPI narcissism vs. Group goal commitment",
       subtitle = "add colours and regression lines for different teams")
```


### Analysis {.tabset}
#### Intercept only model

```{r}
interceptonlymodel <- brm(ggc_mean ~ 1 + (1|team),  
                          data = amber_centered, 
                          warmup = 1000, iter = 3000, 
                          cores = 2, chains = 2, 
                          seed = 123) #to run the model
summary(interceptonlymodel)

# Calculating ICC
hyp <- "sd_team__Intercept^2 / (sd_team__Intercept^2 + sigma^2) = 0"
hypothesis(interceptonlymodel, hyp, class = NULL)
```


#### First level predictors

```{r}
model1 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + (1|team),  
              data = amber_centered, 
              warmup = 1000, iter = 3000, 
              cores = 2, chains = 2, 
              seed = 123) #to run the model

summary(model1)
```

* Fixed regression slopes are not different to 0
* Residual variance on the second level is small (`r round(as.data.frame(VarCorr(model1))$team.sd.Estimate^2, 2)`)


#### First and second level predictors

```{r}
model2 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni + (1|team),
              data = amber_centered, 
              warmup = 1000, iter = 3000, 
              cores = 2, chains = 2, 
              seed = 123) #to run the model

summary(model2)
```


* Fixed regression slope for team_npi is different to 0 (-1.55[-2.86;-0.23])
* All others not different to zero

#### First and second level predictors with random slopes

```{r}
model3 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi + team_cni|team),
              data = amber_centered, 
              warmup = 1000, iter = 3000, 
              cores = 2, chains = 2, 
              seed = 123) #to run the model

summary(model3)
```

#### First and second level predictors with random slopes and cross-level interaction

```{r}
model4 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi + team_cni +
                I(team_npi*team_cni):npi_mean*cni_mean +
                (1 + sex + npi_mean*cni_mean + team_npi + team_cni|team),
              data = amber_centered, 
              warmup = 3000, iter = 8000, 
              cores = 2, chains = 2, 
              seed = 123, control = list(adapt_delta = 0.99))

summary(model4)
```

* The estimate for the intercept is 0.65[-0.68;2.00] NS
* The estimate for the fixed effect of sex (Male) is 0.31[0.05;0.57]

## IGC Task {.tabset}
### Plotting the data {.tabset}
#### Scatter

```{r}
## scatter
ggplot(data  = amber,
       aes(x = npi_mean,
           y = igc_task))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  theme_minimal()+
  labs(title = "NPI narcissism vs. Task conflict")
```


#### Scatter with regression line

```{r}
ggplot(data  = amber,
       aes(x = npi_mean,
           y = igc_task))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  geom_smooth(method = lm,
              se     = FALSE,
              col    = "black",
              size   = .5,
              alpha  = .8)+ # to add regression line
  theme_minimal()+
  labs(title = "NPI narcissism vs. Task conflict",
       subtitle = "add regression line")
```


#### Scatter with regression line by sex

```{r}
ggplot(data  = amber,
       aes(x = npi_mean,
           y = igc_task,
           col = sex,
           group = sex))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  geom_smooth(method = lm,
              # se     = FALSE,
              # col    = "black",
              size   = .5,
              alpha  = .8)+ # to add regression line
  theme_minimal()+
  labs(title = "NPI narcissism vs. Task conflict",
       subtitle = "add regression line")
```


#### Scatter with regression lines coloured by team

```{r}
ggplot(data  = amber,
       aes(x = npi_mean,
           y = igc_task,
           col = as.numeric(team),
           group = team)) +
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter") +# to add some random noise for plotting purposes
  theme_minimal() +
  theme(legend.position = "none") +
  scale_color_gradientn(colours = rainbow(59)) +
  geom_smooth(method = lm,
              se     = FALSE,
              size   = .5,
              alpha  = .8) + # to add regression line
  labs(title = "NPI narcissism vs. Task conflict",
       subtitle = "add colours and regression lines for different teams")
```

### Analysis {.tabset}
#### Intercept only model

```{r}
interceptonlymodel <- brm(igc_task ~ 1 + (1|team),  
                          data = amber_centered, 
                          warmup = 1000, iter = 3000, 
                          cores = 2, chains = 2, 
                          seed = 123) #to run the model
summary(interceptonlymodel)

# Calculating ICC
hyp <- "sd_team__Intercept^2 / (sd_team__Intercept^2 + sigma^2) = 0"
hypothesis(interceptonlymodel, hyp, class = NULL)
```
* Intercept is -.07[-.34;.18]
* ICC = .34[.24;.46] therefore multi-level model is warranted


#### First level predictors

```{r}
model1 <- brm(igc_task ~ 1 + sex + npi_mean * cni_mean + (1|team),  
              data = amber_centered, 
              warmup = 1000, iter = 3000, 
              cores = 2, chains = 2, 
              seed = 123) #to run the model

summary(model1)
```

##### Convergence 

```{r}
model1tranformed <- ggs(model1)

ggplot(filter(model1tranformed, 
              Parameter %in% 
                c("b_Intercept", "b_sexMale", "b_npi_mean", "b_cni_mean",
                  "b_npi_mean:cni_mean")),
       aes(x   = Iteration,
           y   = value, 
           col = as.factor(Chain)))+
  geom_line() +
  geom_vline(xintercept = 1000)+
  facet_grid(Parameter ~ . ,
             scale  = 'free_y',
             switch = 'y')+
  labs(title = "Caterpillar Plots", 
       col   = "Chains")
```

* Trace plots show good mixing with stable means and variances

##### Results

* Fixed effects
  * Intercept = -.14[-.48;.20]
  * sexMale = .19[-.31;.66]
  * npi_mean = .77[.16;1.37]
  * cni_mean = .03[-.10;.16]
  * npi_mean:cni_mean = .04[-.50;.57]


#### First and second level predictors

```{r}
model2 <- brm(igc_task ~ 1 + sex + npi_mean * cni_mean + team_npi + team_cni +
                (1|team),  
              data = amber_centered, 
              warmup = 1000, iter = 3000, 
              cores = 2, chains = 2, 
              seed = 123) #to run the model

summary(model2)
```

##### Convergence 

```{r}
model2tranformed <- ggs(model2)

ggplot(filter(model2tranformed, 
              Parameter %in% 
                c("b_Intercept", "b_sexMale", "b_npi_mean", "b_cni_mean",
                  "b_npi_mean:cni_mean", "b_team_npi", "b_team_cni")),
       aes(x   = Iteration,
           y   = value, 
           col = as.factor(Chain)))+
  geom_line() +
  geom_vline(xintercept = 1000)+
  facet_grid(Parameter ~ . ,
             scale  = 'free_y',
             switch = 'y')+
  labs(title = "Caterpillar Plots", 
       col   = "Chains")
```

* Trace plots show good mixing with stable means and variances

##### Results

* Fixed effects
  * Intercept = -1.59[-4.58;1.57]
  * sexMale = -.11[-.65;.45]
  * npi_mean = .64[.05;1.25]
  * cni_mean = .02[-.12;.16]
  * team_npi = 3.07[-.27;6.27]
  * team_cni = .21[-.61;.99]
  * npi_mean:cni_mean = .08[-.43;.61]
* Variance explained
  * Level1 = -.02
  * Level2 = .15

```{r}
# Variance explained
interceptonlymodel_var <- as.data.frame(VarCorr(interceptonlymodel)) # VarCorr() to extract random effect variances and std devs
model2_var <- as.data.frame(VarCorr(model2))
# level 1
(interceptonlymodel_var$residual__.sd.Estimate^2 - model2_var$residual__.sd.Estimate^2) / interceptonlymodel_var$residual__.sd.Estimate^2
  # level 2
(interceptonlymodel_var$team.sd.Estimate^2 - model2_var$team.sd.Estimate^2) / interceptonlymodel_var$team.sd.Estimate^2

```


#### First and second level predictors with random slopes (1)

```{r}
model3 <- brm(igc_task ~ 1 + sex + npi_mean * cni_mean + team_npi + team_cni +
                (1 + sex + npi_mean * cni_mean + team_npi + team_cni|team),  
              data = amber_centered, 
              warmup = 1000, iter = 3000, 
              cores = 2, chains = 2, 
              seed = 123, control = list(adapt_delta = 0.96))

summary(model3)
```


##### Convergence

```{r}
model3tranformed <- ggs(model3)

ggplot(filter(model3tranformed, 
              Parameter %in% 
                c("b_Intercept", "b_sexMale", "b_npi_mean", "b_cni_mean",
                  "b_npi_mean:cni_mean", "b_team_npi", "b_team_cni")),
       aes(x   = Iteration,
           y   = value, 
           col = as.factor(Chain)))+
  geom_line() +
  geom_vline(xintercept = 1000)+
  facet_grid(Parameter ~ . ,
             scale  = 'free_y',
             switch = 'y')+
  labs(title = "Caterpillar Plots", 
       col   = "Chains")
```

* Trace plots show good mixing with stable means and variances

##### Results

```{r}
stanplot(model3, 
         type = "areas",
         prob = .95)

x <- sjstats::tidy_stan(model3, prob = .95)

x$fixed.conditional
x$`random.conditional.SD/Cor: team`
```


## IGC multivariate
### Analysis {.tabset}
#### Intercept only model

```{r}
interceptonlymodel <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + (1|p|team),  
                          data = amber_centered, 
                          warmup = 1000, iter = 3000, 
                          cores = 2, chains = 2, 
                          seed = 123) #to run the model

fit1 <- add_criterion(interceptonlymodel, "loo")
summary(fit1)

```
* Intercept is -.29[-1.13;.57]
* ICC = .44[.33;.56] therefore multi-level model is warranted


#### First level predictors

```{r}
model1 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + (1|p|team), 
                          data = amber_centered, 
                          warmup = 1000, iter = 3000, 
                          cores = 2, chains = 2, 
                          seed = 123)

fit2 <- add_criterion(model1, "loo")
summary(fit2)
```


#### First and level predictors

```{r}
model2 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + team_npi + team_cni + (1|p|team), 
                          data = amber_centered, 
                          warmup = 1000, iter = 3000, 
                          cores = 2, chains = 2, 
                          seed = 123)

fit3 <- add_criterion(model2, "loo")
summary(fit3)
```


#### First and level predictors with random slopes

```{r}
model3 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 
                1 + sex + npi_mean * cni_mean + team_npi + team_cni + 
                (1 + sex + npi_mean * cni_mean + team_npi + team_cni|p|team), 
                          data = amber_centered, 
                          warmup = 1000, iter = 3000, 
                          cores = 2, chains = 2, 
                          seed = 123)

fit4 <- add_criterion(model3, "loo")
summary(fit4)
```



```{r}
x <- summary(fit4)$fixed %>% 
  as.data.frame() %>% 
  rownames_to_column()

x
```

