---
title: "Amber & Brom MSc data combined"
author: "Will A. S. Hardy"
date: "08/11/2020"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
opts <- options(knitr.kable.NA = "")

##### Packages #####
library(brms) # for the analysis
library(haven) # to load the SPSS .sav file
library(tidyverse) # needed for data manipulation.
library(RColorBrewer) # needed for some extra colours in one of the graphs
library(ggmcmc)
library(ggthemes)
library(ggridges)
library(RcppEigen)
library(knitr)

options(mc.cores = parallel::detectCores() - 1)

##### Data #####
amber1 <- read_rds("../data/amber.rds")

small_team <- 
  amber1 %>% 
  group_by(team) %>% 
  count() %>% 
  arrange(n) %>% 
  filter(n < 5) %>% 
  .$team

amber <- 
  amber1 %>% 
  filter(!team %in% small_team) %>% 
  select(coder, age, sex, sport, team, ggc_mean, starts_with("igc_"), npi_mean,
         cni_mean)

amber_centered <- # Grand mean centering
  amber %>%
  left_join(amber %>% group_by(team) %>%
              summarise(team_npi = mean(npi_mean, na.rm = TRUE), # create team means
                        team_cni = mean(cni_mean, na.rm = TRUE),
                        sd_npi = sd(npi_mean, na.rm = TRUE),
                        sd_cni = sd(cni_mean, na.rm = TRUE),
                        team_igc_proc = mean(igc_proc, na.rm = TRUE),
                        team_igc_rel = mean(igc_rel, na.rm = TRUE),
                        team_igc_task = mean(igc_task, na.rm = TRUE)),
            by = "team") %>% 
  mutate(across(where(is.numeric), ~scale(x = ., scale = FALSE)))


#### Functions ####
# To colour code the extremes, we need to write a small function that calculates the regression lines and adds a column indicating which clusters have the most extreme.
f1 <- function(data, x, y, grouping, n.highest = 3, n.lowest = 3){
  groupinglevel <- data[,grouping]
  res           <- data.frame(coef = rep(NA, length(unique(groupinglevel))), group = unique(groupinglevel))
  names(res)    <- c("coef", grouping)
  groups <- as.character(unlist(unique(c(groupinglevel))))
  for(i in 1:length(unique(groupinglevel))){
    data2    <- as.data.frame(data[data[,grouping] == groups[i],])
    res[i,1] <- as.numeric(lm(data2[, y] ~ data2[, x])$coefficients[2])
  }
  top    <- res %>% top_n(n.highest, coef)
  bottom <- res %>% top_n(-n.lowest, coef)
  res <- res %>% 
    mutate(high_and_low = ifelse(coef %in% top$coef, "top",  
                                 ifelse(coef %in% bottom$coef, "bottom", "none")))
  data3  <- left_join(data, res)
  return(data3)
}


modelParams <- function(model){
  posterior_summary(model) %>% 
  as_tibble(rownames = NA) %>% 
  rownames_to_column(var = "Parameter") %>% 
  filter(!str_detect(Parameter, "r_team"),
         !str_detect(Parameter, "L_"),
         !str_detect(Parameter, "z_"))
}

bayesEstimate <- function(.){
  require(papaja)
  paste0(printnum(.$Estimate), "[", printnum(.$Q2.5), ",", printnum(.$Q97.5), "]")
}
```


## Team level summary

```{r, team-summary}
amber_centered %>% 
  group_by(team) %>% 
  summarise(across(.cols = where(is.numeric), .fns = ~mean(.x, na.rm = TRUE))) %>% 
  kable(digits = 2)
```


## Group goal commitment {.tabset}
### Plotting the data {.tabset}
#### Scatter

```{r, npi-ggc-mean-scatter}
## scatter
ggplot(data  = amber,
       aes(x = npi_mean,
           y = ggc_mean))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  theme_minimal()+
  labs(title = "NPI narcissism vs. Group conflict")
```


#### Scatter with regression line

```{r, npi-ggc-mean-scatter-reg-line}
ggplot(data  = amber,
       aes(x = npi_mean,
           y = ggc_mean))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  geom_smooth(method = lm,
              se     = FALSE,
              col    = "black",
              size   = .5,
              alpha  = .8)+ # to add regression line
  theme_minimal()+
  labs(title = "NPI narcissism vs. Group conflict",
       subtitle = "add regression line")
```


#### Scatter with regression line by sex

```{r, npi-ggc-mean-scatter-sex-reg-line}
ggplot(data  = amber,
       aes(x = npi_mean,
           y = ggc_mean,
           col = sex,
           group = sex))+
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter")+# to add some random noise for plotting purposes
  geom_smooth(method = lm,
              # se     = FALSE,
              # col    = "black",
              size   = .5,
              alpha  = .8)+ # to add regression line
  theme_minimal()+
  labs(title = "NPI narcissism vs. Group conflict",
       subtitle = "add regression line")
```


#### Scatter with regression lines coloured by team

##### NPI

```{r, npi-ggc-mean-scatter-team-reg-line}
ggplot(data  = amber,
       aes(x = npi_mean,
           y = ggc_mean,
           col = as.numeric(team),
           group = team)) +
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter") +# to add some random noise for plotting purposes
  theme_minimal() +
  theme(legend.position = "none") +
  scale_color_gradientn(colours = rainbow(59)) +
  geom_smooth(method = lm,
              se     = FALSE,
              size   = .5,
              alpha  = .8) + # to add regression line
  labs(title = "NPI narcissism vs. Group goal commitment",
       subtitle = "add colours and regression lines for different teams")
```


##### CNI

```{r, cni-ggc-mean-scatter-team-reg-line}
ggplot(data  = amber,
       aes(x = cni_mean,
           y = ggc_mean,
           col = as.numeric(team),
           group = team)) +
  geom_point(size = 1.2,
             alpha = .8,
             position = "jitter") +# to add some random noise for plotting purposes
  theme_minimal() +
  theme(legend.position = "none") +
  scale_color_gradientn(colours = rainbow(59)) +
  geom_smooth(method = lm,
              se     = FALSE,
              size   = .5,
              alpha  = .8) + # to add regression line
  labs(title = "CNI narcissism vs. Group goal commitment",
       subtitle = "add colours and regression lines for different teams")
```


### Analysis 1 {.tabset}
#### Intercept only model

```{r, ggc-int-model, include=FALSE}
ggc_interceptonlymodel <- 
  brm(ggc_mean ~ 1 + (1|team),  
      data = amber_centered, 
      warmup = 1000, iter = 3000, seed = 123) 

ggc_interceptonlyparams <- modelParams(ggc_interceptonlymodel)

# Calculating ICC
hyp <- "sd_team__Intercept^2 / (sd_team__Intercept^2 + sigma^2) = 0"
hypothesis(ggc_interceptonlymodel, hyp, class = NULL)
icc_test <- print(hypothesis(ggc_interceptonlymodel, hyp, class = NULL))
icc_est <- paste0(icc_test$hypothesis$Estimate, " [", icc_test$hypothesis$CI.Lower, ",",
       icc_test$hypothesis$CI.Upper, "]")
```


```{r, ggc-int-params}
ggc_interceptonlyparams %>% 
  kable(digits = 2)
```

* Posterior mean of residual variance at team level = `r ggc_interceptonlyparams[2,2]^2`
* Posterior mean of residual variance at individual level = `r ggc_interceptonlyparams[3,2]^2`
* ICC: $\rho$ = `r icc_est`


#### First level predictors

```{r, ggc-l1-model, interval=FALSE}
ggc_model1 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + (1|team),  
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123) 

ggc_model1params <- modelParams(ggc_model1)
```


```{r, ggc-l1-params}
broom.mixed::tidy(ggc_model1) %>% 
  kable()
```

* NS npi_mean
* Positive effect for CNI mean
* NS interaction
* Residual variance on the team level : $\sigma_{u0}$ = `r ggc_model1params[6,2]^2`)



#### First level predictors with random slopes

```{r, ggc-l1-rand-slopes-model, include=FALSE}
ggc_model2 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                    (1 + sex + npi_mean*cni_mean |team),
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123)

ggc_model2params <- modelParams(ggc_model2)
```


```{r ggc-l1-rand-slopes-params}
broom.mixed::tidy(ggc_model2) %>% 
  kable()
```

* NPI mean NS, variance of slopes = `r ggc_model2params[8,2]^2`
* CNI mean positive, variance of slopes = `r ggc_model2params[9,2]^2`
* Interaction NS
* Residual variance on the team level : $\sigma_{u0}$ = `r ggc_model2params[6,2]^2`


#### First and second level predictors with random slopes

```{r, ggc-l1and2-rand-slopes-model, include=FALSE}
ggc_model3 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean + 
                team_npi * team_cni + 
                (1 + sex + npi_mean*cni_mean|team),
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123)

ggc_model3params <- modelParams(ggc_model3)
```


```{r, ggc-l1and2-rand-slopes-params}
broom.mixed::tidy(ggc_model3) %>% 
  kable()
```

* Positive effect for sexMale, variance of slopes = `r ggc_model3params[10,2]^2`
* NPI mean NS, variance of slopes = `r ggc_model3params[11,2]^2`
* CNI mean NA, variance of slopes = `r ggc_model3params[12,2]^2`
* Team NPI negative
* Team CNI NS
* L1 Interaction NS
* L2 Interaction NS
* Residual variance on the team level : $\sigma_{u0}$ = `r ggc_model3params[9,2]^2` 
  

#### First and second level predictors with random slopes and cross-level interaction

```{r, ggc-l1and2-rand-slopes-xlevl-model, include=FALSE}
ggc_model4 <- brm(ggc_mean ~ 1 + sex + npi_mean*cni_mean*team_npi*team_cni +
                    (1 + sex + npi_mean*cni_mean|team),
                  data = amber_centered, 
                  warmup = 3000, iter = 8000,
                  seed = 123, control = list(adapt_delta = 0.99))

ggc_model4params <- modelParams(ggc_model4) 
```


```{r, ggc-l1and2-rand-slopes-xlevl-convergence, dependson="ggc-l1and2-rand-slopes-xlevl-model"}
plot(ggc_model4,N = 1, ask = FALSE)

```


```{r, ggc-l1and2-rand-slopes-xlevl-params, dependson="ggc-l1and2-rand-slopes-xlevl-model"}
broom.mixed::tidy(ggc_model4) %>% 
  kable()

conditional_effects(ggc_model4)
```

* Positive effect for sexMale, variance of slopes = `r ggc_model3params[10,2]^2`
* NPI mean NS, variance of slopes = `r ggc_model3params[11,2]^2`
* CNI mean NS, variance of slopes = `r ggc_model3params[12,2]^2`
* Team NPI negative
* Team CNI NS
* L1 Interaction NS
* L2 Interaction NS
* Residual variance on the team level : $\sigma_{u0}$ = `r ggc_model3params[9,2]^2` 


```{r, ggc-l1and2-rand-slopes-xlevl-int-plot, dependson="ggc-l1and2-rand-slopes-xlevl-model"}
pred_data <- function(data, variable){
  
  variable <- enquo(variable)
  
  data %>%
    summarise(low = mean(!!variable, na.rm = TRUE) - 
                sd(!!variable, na.rm = TRUE),
              high = mean(!!variable, na.rm = TRUE) +
                sd(!!variable, na.rm = TRUE)) %>% 
    unlist()
  
}


sex <- factor(c("Female", "Male"), levels = c("Female", "Male"))
npi_mean <- pred_data(amber_centered, npi_mean)
cni_mean <- pred_data(amber_centered, cni_mean)
team_npi <- pred_data(amber_centered, team_npi)
team_cni <- pred_data(amber_centered, team_cni)
team <- unique(amber_centered$team)

new_data <- 
  map_dfr(.x = 1:length(team), 
          .f = ~tibble(sex = c(rep(sex[1], 16), rep(sex[2], 16)),
                       npi_mean = 
                         rep(c(rep(npi_mean[1], 8), rep(npi_mean[2], 8)), 2),
                       cni_mean = 
                         rep(c(rep(cni_mean[1], 4), rep(cni_mean[2], 4)), 4),
                       team_npi = 
                         rep(c(rep(team_npi[1], 2), rep(team_npi[2], 2)), 8),
                       team_cni = rep(team_cni, 16),
                       team = rep(team[.x], 32))) %>% 
  mutate(sex = case_when(sex == 1 ~ "Female",
                         sex == 2 ~ "Male"))

df <- tidybayes::predicted_draws(ggc_model4, newdata = new_data, n = 1000) %>% 
  group_by(npi_mean, cni_mean, team_npi, team_cni) %>% 
  summarise(npi_mean = npi_mean,
            cni_mean = cni_mean,
            team_npi = team_npi,
            team_cni = team_cni,
            GGC = mean(.prediction),
            sd_pred = sd(.prediction),
            .groups = "drop") 

df %>%
  mutate(cni_mean = 
           case_when(cni_mean == max(cni_mean) ~ 
                       paste("High", round(max(cni_mean), 3)),
                     cni_mean == min(cni_mean) ~ 
                       paste("Low", round(min(cni_mean), 3))),
         team_npi = 
           case_when(team_npi == max(team_npi) ~ 
                       paste("High team NPI", round(max(team_npi), 3)),
                     team_npi == min(team_npi) ~ 
                       paste("Low team NPI", round(min(team_npi), 3))),
         team_cni = 
           case_when(team_cni == max(team_cni) ~ 
                       paste("High team CNI", round(max(team_cni), 3)),
                     team_cni == min(team_cni) ~ 
                       paste("Low team CNI", round(min(team_cni), 3)))) %>%
  ggplot(aes(x = npi_mean, y = GGC, colour = cni_mean)) +
  geom_line() +
  geom_point() +
  facet_wrap(~team_npi + team_cni) +
  labs(caption = "Variables are grand mean centred,\n therefore scores of 0 represent the mean individual or team. \nHigh and low values are ±1 SD.")

```



```{r, ggc-team-npi-plot}
amber_centered %>% 
  ggplot(aes(x = npi_mean, y = ggc_mean, 
             col = (team_npi), group = team)) +
  viridis::scale_color_viridis() +
  geom_point(size = .7, alpha = .8, position = "jitter") +
  geom_smooth(method = "lm",
              se = FALSE, size = .8, alpha = .8) + 
  theme_minimal() +
  labs(title = "Linear relationship for teams with different levels of team NPI",
       subtitle = "The linear relationship is not the same for all teams",
       col = "Team NPI")
```

```{r, ggc-team-npi-plot-bayes}
simple_npi_model_1 <- 
  brm(ggc_mean ~ 1 + npi_mean + (1 + npi_mean | team),
      data = amber_centered,
      warmup = 1000, iter = 5000, chains = 2,
      seed = 123, control = list(adapt_delta = .96),
      save_all_pars = TRUE, cores = 2)

posterior_simple_npi_model_1 <- 
  posterior_samples(simple_npi_model_1, pars = "npi_mean")[,-c(1:3)] %>%
  t() %>% 
  as_tibble()

team_npi_scores <- 
  amber_centered %>% 
  group_by(team) %>% 
  summarise(team_npi_2 = mean(team_npi))

posterior_simple_npi_model_1_long <- 
  bind_cols(team_npi_scores, posterior_simple_npi_model_1) %>% 
  pivot_longer(cols = colnames(posterior_simple_npi_model_1), 
               names_to = "Team") %>% 
  group_by(team) %>% 
  mutate(mean_per_team = mean(value)) %>% 
  ungroup

posterior_simple_npi_model_1_long %>% 
  ggplot() +
  ggridges::geom_density_ridges(aes(x = value, 
                                    y = reorder(as.factor(team), mean_per_team),
                                    height = ..density..,
                                    fill = as.factor(round(team_npi_2, 2))),
                                scale = 3, alpha = .6) +
  scale_x_continuous(limits = c(-1.5,1.5)) +
  geom_point(data = summarise(group_by(posterior_simple_npi_model_1_long, team),
                              mean = mean(mean_per_team)), 
             aes(x = mean, y = as.factor(team)), size = 1, col = "red") +
  viridis::scale_fill_viridis(discrete = TRUE) +
  geom_vline(xintercept = 0, col = "red") +
  labs(fill = "Team NPI", y = "Teams", 
       title = expression(paste("Team Level Error of Regression Coefficient of NPI on GGC (", u["2j"],")")),
       subtitle = expression(paste("posterior distribution of team level error of regression coefficient (", u["2j"],") per team with the means in red")), 
       caption  = expression(paste("Regression formula: GGC = ", gamma["00"], "+", gamma["20"],"*", npi["ij"], "+", u["2j"], "*", npi["ij"],"+", e["ij"] )))+
  annotate(geom     = "text", 
           x        = 0, 
           y        = 1.5, 
           label    = "Grand mean", 
           col      = "red", 
           family   = theme_get()$text[["family"]], 
           size     = theme_get()$text[["size"]]/3, 
           fontface = "italic")+
  theme_tufte()
  
```


```{r}
distance95 <- 
  posterior_simple_npi_model_1_long %>% 
  group_by(team) %>% 
  summarise(l95 = quantile(value, probs = .025),
            u95 = quantile(value, probs = .975),
            distance = u95-l95,
            mean_estimate = mean(value)) %>% 
  bind_cols(team_npi_scores) %>% 
  group_by(team_npi_2) %>% 
  summarise(mean = mean(distance),
            mean_estimate = mean(mean_estimate),
            lower = mean(l95),
            upper = mean(u95),
            mean_cci = paste("[",sprintf("%.4f",round(lower,4)), ":", sprintf("%.4f",round(upper,4)), "]")) %>% 
  mutate(quadratic = team_npi_2^2)

model1 <- lm(mean ~ team_npi_2, data = distance95)
model2 <- lm(mean ~ team_npi_2 + quadratic, data = distance95)

summary(model1)
summary(model2) # Quadratic term not significant

dat <- data.frame(team_npi_2 = c(seq(-.18, .22, .01)),
                  quadratic = seq(-.18, .22, .01)^2)

dat$yhat <- predict(model1, dat)

ggplot() +
  geom_line(data = dat, 
            aes(x = team_npi_2, y = yhat), lty = "dotted", size = 1) +
  geom_point(data = distance95,
             aes(x = team_npi_2, y = mean, col = mean_estimate)) +
  geom_text(data = distance95,
            aes(x = team_npi_2, y = mean, label = mean_cci),
                hjust    = .5, 
                vjust    = -.15, 
                family   = theme_get()$text[["family"]], 
                size     = 2, 
                fontface = "italic") +
  annotate(geom = "text", x = .1, y = 2.85,
           label = "CCI distance = 2.37 - 1.51*team NPI",
           colour   = "black",  
           family   = theme_get()$text[["family"]], 
           size     = 2, 
           fontface = "italic") +
  viridis :: scale_color_viridis(discrete = F, direction = -1) +
  labs(y = "95% CCI distance",
       title = expression(paste("Mean CCI Distance of Posterior of (", u["2j"], ") for Different levels of team NPI")),
       subtitle = "In brackets the actual CCIs and in colour the parameter estimate",
       col = expression(paste("estimate ", u["2j"]))) +
  theme_tufte()
```



#### Model comparison

```{r, ggc-model-comparison, cache=FALSE}
bind_rows(broom.mixed::tidy(ggc_model1),
          broom.mixed::tidy(ggc_model2),
          broom.mixed::tidy(ggc_model3),
          broom.mixed::tidy(ggc_model4),.id = "model") %>% 
  mutate(est_print = paste(paste0(round(estimate, 2), "[", round(conf.low, 2),
                                  ",", round(conf.high, 2), "]"))) %>% 
  pivot_wider(values_from = est_print, names_from = model,
              id_cols = term) %>% 
  kable(digits = 2)
```


## IGC multivariate {.tabset}

### Plotting

```{r, eval=TRUE}
plotSlopes <- function(data, resp, efflist, group) {
  require(ggplot2)
  require(purrr)
  y <- enquo(resp)
  group <- enquo(group)
  ngroups <- data %>% 
    select(!!group) %>% 
    unique() %>% 
    nrow()

  map(efflist, function(x)
    ggplot(data, aes(!!sym(x), !!y, col = as.numeric(!!group), 
                     group = !!group)) +
    geom_point(size = 1.2,
               alpha = .8,
               position = "jitter") + # to add some random noise for plotting purposes
    theme_minimal() +
    theme(legend.position = "none") +
    scale_color_gradientn(colours = rainbow(n = ngroups)) +
    geom_smooth(method = lm,
                se     = FALSE,
                size   = .5,
                alpha  = .8) + # to add regression line
    ylab(NULL)
  )
}
```


#### NPI

```{r}
plotSlopes(amber, resp = npi_mean, 
           efflist = c("igc_task", "igc_rel", "igc_proc"),
           group = team) %>% 
  gridExtra::grid.arrange(grobs = ., left = "npi_mean")
```


#### CNI

```{r}
plotSlopes(amber, resp = cni_mean, 
           efflist = c("igc_task", "igc_rel", "igc_proc"),
           group = team) %>% 
  gridExtra::grid.arrange(grobs = ., left = "cni_mean")
```



### Analysis {.tabset}
#### Intercept only model

#### First and second level predictors with random slopes and cross-level interaction

```{r, igc-l1and2-rand-slopes-xlevl-model, include=FALSE}
ggc_model4 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + sex + npi_mean*cni_mean*team_npi*team_cni +
                    (1 + sex + npi_mean*cni_mean|p|team),
                  data = amber_centered, 
                  warmup = 3000, iter = 8000,
                  seed = 123, control = list(adapt_delta = 0.99))

ggc_model4params <- modelParams(ggc_model4) 
```


```{r, igc-l1and2-rand-slopes-xlevl-params, dependson="ggc-l1and2-rand-slopes-xlevl-model"}
broom.mixed::tidy(ggc_model4) %>% 
  kable()

conditional_effects(ggc_model4)
```

--- 

try `capture.output()`

```{r, include=FALSE, eval=FALSE}
igc_interceptonlymodel <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + (1|p|team),  
                          data = amber_centered, 
                          warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

# x <- sjstats::tidy_stan(interceptonlymodel, prob = .95)
# 
# bind_rows(x$fixed.conditional..igcproc,
# x$fixed.conditional..igcrel,
# x$fixed.sigma..igcrel,
# x$fixed.conditional..igctask,
# x$fixed.sigma..igctask
# ) %>% 
#   pivot_wider(id_cols = Cleaned_Parameter, names_from = Response, values_from = c(Estimate, Std.Error, `HDI(95%)`))
```


```{r, eval=FALSE}
igc_interceptonlyparams <- modelParams(igc_interceptonlymodel)

igc_interceptonlyparams %>% 
  kable(digits = 2)
```



#### First level predictors

```{r, include = FALSE, eval=FALSE}
igc_model1 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + (1|p|team), 
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

igc_model1params <- modelParams(igc_model1)
```


```{r, eval=FALSE}
igc_model1params %>% 
  kable(digits = 2)
```


#### First and second level predictors

```{r, include = FALSE, eval=FALSE}
igc_model2 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + team_npi + team_cni + (1|p|team), 
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

igc_model2params <- modelParams(igc_model2)
```


```{r, eval=FALSE}
igc_model2params %>% 
  kable(digits = 2)
```



#### First and second level predictors with L1 random slopes

```{r, eval=FALSE}
igc_model3 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + team_npi + team_cni + (1 + 
                sex + npi_mean * cni_mean|p|team), 
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123, save_all_pars = TRUE) 

igc_model3params <- modelParams(igc_model3)
```


```{r, eval=FALSE}
igc_model3params %>% 
  kable(digits = 2)

conditional_effects(igc_model3)
```




#### First and level predictors with L1 interaction and L2 random slopes

```{r, eval=FALSE}
igc_model4 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean * cni_mean + team_npi + team_cni + (1 + 
                sex + npi_mean * cni_mean + team_npi + team_cni|p|team), 
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123,
              control = list(adapt_delta = 0.99), save_all_pars = TRUE) 

igc_model4params <- modelParams(igc_model4)
```


```{r, eval=FALSE}
igc_model4params %>% 
  kable(digits = 2)

conditional_effects(igc_model4)
```


#### First and level predictors with L2 interaction and L2 random slopes

```{r, eval=FALSE}
igc_model5 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean*cni_mean + team_npi*team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi*team_cni|p|team), 
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123,
              control = list(adapt_delta = 0.99), save_all_pars = TRUE) 

igc_model5params <- modelParams(igc_model5)
```


```{r, eval=FALSE}
igc_model5params %>% 
  kable(digits = 2)

conditional_effects(igc_model5)
```

#### First and level predictors with L2 interaction and L2 random slopes and partial cross level interaction

```{r, eval=FALSE}
igc_model6 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean*cni_mean:team_npi*team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi*team_cni|p|team), 
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123,
              control = list(adapt_delta = 0.99), save_all_pars = TRUE) 

igc_model6params <- modelParams(igc_model6)
```


```{r, eval=FALSE}
igc_model6params %>% 
  kable(digits = 2)

conditional_effects(igc_model6)
```


#### First and level predictors with L2 interaction and L2 random slopes and full cross level interaction

```{r, eval=FALSE}
igc_model7 <- brm(mvbind(igc_task, igc_rel, igc_proc) ~ 1 + 
                sex + npi_mean*cni_mean*team_npi*team_cni + 
                (1 + sex + npi_mean*cni_mean + team_npi*team_cni|p|team), 
              data = amber_centered, 
              warmup = 1000, iter = 3000, seed = 123,
              control = list(adapt_delta = 0.99), save_all_pars = TRUE) 

igc_model7params <- modelParams(igc_model7)
```


```{r, eval=FALSE}
igc_model7params %>% 
  kable(digits = 2)

conditional_effects(igc_model7)
```


